Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-10-06 main.tex
delete old paragraph

%\subsection{\cye{Potential for the gradient operator and the corresponding Poincar\'e--Friedrichs inequality}} \label{subsection:intro_grad}

@@

%\subsection{\cye{Potentials for the curl and divergence operators and the corresponding Poincar\'e--Friedrichs inequalities}} \label{section:intro_curl_div}

@@

%\subsection{\cye{Potentials for the exterior derivative and the corresponding Poincar\'e--Fried\-richs inequalities}} \label{section:intro_EC}

@@

%\subsection{\cye{Numerically computed guaranteed bounds on Poincar\'e--Friedrichs constants seen as eigenvalues}}

@@

%\subsection{\cye{Objectives and methodology}}

@@

% \subsubsection{\cye{Combinatorial constants over face-connected triangulated domains}}

@@

%\subsubsection{\cye{Combinatorial constants over shellable triangulated domains}}

@@

%\subsubsection{\cye{Analytical constants over convex domains}}

@@

%\subsubsection{\cye{Domains star-shaped with respect to a ball}}

@@

%\subsubsection{\cye{Potentials subject to partial boundary conditions}}

@@

%\subsection{\cye{Main results}}

@@

There are several avenues for further research going from here. 
The upper bounds in this manuscript are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches. There are at least two points where the present techniques can be improved further. First, we utilize local Poincar\'e--Friedrichs constants over single simplices, subject to various boundary conditions, but these local estimates over convex domains likely leave room for improvement.
Second, our construction needs to extend differential forms onto a simplex from the complement of that simplex inside a local star. In the present manuscript, this is achieved via pullback along a bi-Lipschitz mapping. 
Better transformations or more careful estimates are likely possible, as are completely different approaches.  For example, it is likely that further research on trace and extension operators on triangulations will enable better estimates.

Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains. We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators. 
On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest. 
These topics remain for future research.

Estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is fundamentally restricted to spaces with the simplicial homology groups of disks and spheres. In particular, domains with shellable triangulations are contractible. However, these estimates are important partial results. Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds. 
\\

>>>>

\subsection{\cye{Potential for the gradient operator and the corresponding Poincar\'e--Friedrichs inequality}} \label{subsection:intro_grad}

@@

\subsection{\cye{Potentials for the curl and divergence operators and the corresponding Poincar\'e--Friedrichs inequalities}} \label{section:intro_curl_div}

@@

\subsection{\cye{Potentials for the exterior derivative and the corresponding Poincar\'e--Fried\-richs inequalities}} \label{section:intro_EC}

@@

\subsection{\cye{Numerically computed guaranteed bounds on Poincar\'e--Friedrichs constants seen as eigenvalues}}

@@

\subsection{\cye{Objectives and methodology}}

@@

\subsubsection{\cye{Combinatorial constants over face-connected triangulated domains}}

@@

\subsubsection{\cye{Combinatorial constants over shellable triangulated domains}}

@@

\subsubsection{\cye{Analytical constants over convex domains}}

@@

\subsubsection{\cye{Domains star-shaped with respect to a ball}}

@@

\subsubsection{\cye{Potentials subject to partial boundary conditions}}

@@

\subsection{\cye{Main results}}

@@
